timesliced_random_cell_selection

### 2018-11-08 src/raster_sjl.Rmd
working of depth being NA....

>>>>

check the values for all layers manually

```{r}
test <- read.csv("../data/observationslong.csv", header = TRUE)
testrow1 <- test[1, ]
testrow1
#testrow1$month <- sprintf("%02d",testrow1$month)
testrow1xy <- testrow1[ ,c(4,5)] # This is to tell R where the coordinates are (in column 4 and 5). Note that the column order needs to be longitude, latitude
testrow1sp <- SpatialPointsDataFrame(coords = testrow1xy, data = testrow1, proj4string = CRS("+proj=aea +lat_1=50 +lat_2=70 +lat_0=40 +lon_0=-60 +x_0=0 +y_0=0 +ellps=GRS80 +datum=NAD83 +units=m +no_defs")) # The CRS is used here is for the albers equal area projection.
test10 <- extract(x=row1rast[[10]], y = testrow1sp)
test10
testrow2 <- test[2, ]
#testrow2$month <- sprintf("%02d",testrow2$month)
testrow2xy <- testrow2[ ,c(4,5)] # This is to tell R where the coordinates are (in column 4 and 5). Note that the column order needs to be longitude, latitude
testrow2sp <- SpatialPointsDataFrame(coords = testrow2xy, data = testrow2, proj4string = CRS("+proj=aea +lat_1=50 +lat_2=70 +lat_0=40 +lon_0=-60 +x_0=0 +y_0=0 +ellps=GRS80 +datum=NAD83 +units=m +no_defs")) # The CRS is used here is for the albers equal area projection.
test12 <- extract(x=row1rast[[12]], y = testrow2sp)
test12
testrow3 <- test[3, ]
testrow3xy <- testrow3[ ,c(4,5)] # This is to tell R where the coordinates are (in column 4 and 5). Note that the column order needs to be longitude, latitude
testrow3sp <- SpatialPointsDataFrame(coords = testrow3xy, data = testrow3, proj4string = CRS("+proj=aea +lat_1=50 +lat_2=70 +lat_0=40 +lon_0=-60 +x_0=0 +y_0=0 +ellps=GRS80 +datum=NAD83 +units=m +no_defs")) # The CRS is used here is for the albers equal area projection.
testrow3sp
test40 <- extract(x=row3rast[[40]], y = testrow3sp)
test40
testrow4 <- test[4, ]
testrow4xy <- testrow4[ ,c(4,5)] # This is to tell R where the coordinates are (in column 4 and 5). Note that the column order needs to be longitude, latitude
testrow4sp <- SpatialPointsDataFrame(coords = testrow4xy, data = testrow4, proj4string = CRS("+proj=aea +lat_1=50 +lat_2=70 +lat_0=40 +lon_0=-60 +x_0=0 +y_0=0 +ellps=GRS80 +datum=NAD83 +units=m +no_defs")) # The CRS is used here is for the albers equal area projection.
testrow4sp
test18 <- extract(x=row3rast[[18]], y = testrow4sp)
test18
testrow5 <- test[5, ]
testrow5xy <- testrow5[ ,c(4,5)] # This is to tell R where the coordinates are (in column 4 and 5). Note that the column order needs to be longitude, latitude
testrow5sp <- SpatialPointsDataFrame(coords = testrow5xy, data = testrow5, proj4string = CRS("+proj=aea +lat_1=50 +lat_2=70 +lat_0=40 +lon_0=-60 +x_0=0 +y_0=0 +ellps=GRS80 +datum=NAD83 +units=m +no_defs")) # The CRS is used here is for the albers equal area projection.
test27 <- extract(x=row3rast[[27]], y = testrow5sp)
test27
testrow6 <- test[6, ]
testrow6xy <- testrow6[ ,c(4,5)] # This is to tell R where the coordinates are (in column 4 and 5). Note that the column order needs to be longitude, latitude
testrow6sp <- SpatialPointsDataFrame(coords = testrow6xy, data = testrow6, proj4string = CRS("+proj=aea +lat_1=50 +lat_2=70 +lat_0=40 +lon_0=-60 +x_0=0 +y_0=0 +ellps=GRS80 +datum=NAD83 +units=m +no_defs")) # The CRS is used here is for the albers equal area projection.
test1 <- extract(x=row2rast[[1]], y = testrow6sp)
test1
testrow7 <- test[7, ]
testrow7xy <- testrow7[ ,c(4,5)] # This is to tell R where the coordinates are (in column 4 and 5). Note that the column order needs to be longitude, latitude
testrow7sp <- SpatialPointsDataFrame(coords = testrow7xy, data = testrow7, proj4string = CRS("+proj=aea +lat_1=50 +lat_2=70 +lat_0=40 +lon_0=-60 +x_0=0 +y_0=0 +ellps=GRS80 +datum=NAD83 +units=m +no_defs")) # The CRS is used here is for the albers equal area projection.
test5 <- extract(x=row2rast[[5]], y = testrow7sp)
test5
```

and surface...
```{r}
test1.1 <- extract(x=row1rast[[1]], y = testrow1sp)
test2.1 <- extract(x=row1rast[[1]], y = testrow2sp)
test3.1 <- extract(x=row3rast[[1]], y = testrow3sp)
test3.1
test4.1 <- extract(x=row3rast[[1]], y = testrow4sp)
test4.1
test5.1 <- extract(x=row3rast[[1]], y = testrow5sp)
test5.1
test6.1 <- extract(x=row2rast[[1]], y = testrow6sp)
test6.1
test7.1 <- extract(x=row2rast[[1]], y = testrow7sp)
test7.1
```
pull up values you got from the loop...
```{r}
obssp$salinity_depth
```

```{r}
obssp$salinity_surface
```
ok so the loop works for repetitive years and months

now all the depth values were numbered - in reality I have some NA. How to deal...
.csv altered to include 1 NA

```{r}
netcdf_list <- list.files("../data/env/testnetcdf/salinity", pattern = '*.nc', full.names = TRUE) #true means the full path is included
no_netcdf <- length(netcdf_list) #for the loop - need to know how many files to cycle through
netcdf_name <- list.files("../data/env/testnetcdf/salinity", pattern = '*.nc', full.names = FALSE) #false means the path is not included
library (ncdf4)
for (i in 1:no_netcdf){  
  print(netcdf_name[i]) #this just prints the name of the netCDF R is working one
  brkyr <- as.integer(sapply(strsplit(netcdf_name[i], "_"), "[[", 1)) # extracting the first part of the netcdf filename (which is the year)
  brkmth <- as.integer(sapply(strsplit(netcdf_name[i], "_"), "[[", 2)) # extracting the second part of the netcdf filename (which is the month)
  temp_brick <- brick(netcdf_list[i], lvar = 4)
  temp_brick <- projectRaster(temp_brick, aea) 
    for (j in 1:nrow(obssp)) {  
      print (j)
      de <- obssp$depth[[j]]  # a variable for the observation depth layer
      yr <- (obssp$year[j])  # a variable for the observation year
      mth <- (obssp$month[j])  # a variable for the observation month
      #I think i need an if statement here... if brkyr == yr & brkmth == mth do the data extraction below
        #for (k in 1:nrow(obssp)){
          if (brkyr == yr & brkmth == mth){
            obssp$salinity_surface[j] <- extract(x=temp_brick[[1]], y = obssp[j, ]) 
            if (is.na(de)){
              obssp$salinity_depth <- NA
            } else (de >= 1) {
              obssp$salinity_depth[j] <- extract(x=temp_brick[[de]], y = obssp[j, ])
            }
           }

```{r}
obssp$salinity_depth
```
